Capstone Movielens Report

### 2025-11-25 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report section [UME Model Regularization: Fine-tuning\: review.

::: {.noteblock data-latex=""}
In the code snippet above we use the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function described in the [UME Model Utility Functions] section of [Appendix A: Support Functions].
:::

@@

  - [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) (described in the [UME Model Utility Functions] section) to calculate the *RMSE* for the *Current Model*;

@@

::: {.noteblock data-latex=""}
The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) are described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UME Model Regularization] of [Appendix A: Support Functions], respectively.
:::

@@

UM_effect.loop_starter <- c(endpoints["start"], 
                            endpoints["end"], 
                            8)
UM_effect.loop_starter
#> [1] 0.3 0.5 8.0

UME.rglr.fine_tune.cache.base_name <- "UME.rglr.fine-tune"

@@

::: {.noteblock data-latex=""}
The complete version of the source code provided in this section can be also found in the [Fine-tuning Step of the Regularization Method for the User+Movie Model](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L867) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
:::

>>>>

::: {.noteblock data-latex=""}
In the code snippet above we use the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) function described in the [UME Model: Utility Functions] section of [Appendix A: Support Functions].
:::

@@

  - [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) (described in the [UME Model: Utility Functions] section) to calculate the *RMSE* for the *Current Model*;

@@

::: {.noteblock data-latex=""}
The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) are described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UME Model: Regularization] of [Appendix A: Support Functions], respectively.
:::

@@

UM_effect.loop_starter <- c(endpoints["start"], 
                            endpoints["end"], 
                            8)
UME.rglr.fine_tune.cache.base_name <- "UME.rglr.fine-tune"
```
```{r}
print(UM_effect.loop_starter)
print(UME.rglr.fine_tune.cache.path)
print(UME.rglr.fine_tune.cache.base_name)
class(regularize.test_lambda.UM_effect.cv)
```
```{r, eval=FALSE}

@@

::: {.noteblock data-latex=""}
The helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) used in code snippet above is described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) of [Appendix A: Support Functions].
:::
